An Ant Cuticle Texture Classification Algorithm for Ecological Anaylsis

### 2021-09-03 paper/paper.tex
adjust experiment 1 table

@@

In the first experiment, we investigate the ability of a basic CNN to classify
cuticle texture into the two main categories: \textit{rough} and
\textit{smooth}. The goal of this experiment is to determine if more intricate
data preprocessing is necessary to classify the texture of the ant. Images were
resized to different sizes for CNN input and different samples per class were
also tested.The dataset used is shown in Table \ref{table:classdist_rs_full},
and the results are shown in Table \ref{table:exp1_full}.

>>>>

\section{Related Work}

\section{Proposed Approach}

@@

In the first experiment, we investigate the ability of a basic CNN to classify
cuticle texture into the two main categories: \textit{rough} and
\textit{smooth}. The goal of this experiment is to determine if more intricate
data preprocessing or a more powerful model is necessary to classify the texture
of the ant. Images were resized to different sizes for CNN input and different
samples per class were also tested. The dataset used is shown in Table
\ref{table:classdist_rs_full}, and the results are shown in Table
\ref{table:exp1_full}.
